Workflow

### 2014-07-26 Workflow/Workflow.Rmd
More improvements to Workflow.Rmd.

### Post-process the results
* Run `PostProcess.R -R data_resample/<Source>` on dahl to create:       
    + `Packages/EconData/data/<Source>_Coeffs.rda` and
    + `Packages/EconData/data/<Source>_Fitted.rda`.

Note that this command will need to be issued from a node of the cluster (e.g., node-00), not from `fs1.calvin.edu`.

>>>>

### Post-process the results
* Run `PostProcess.R -R data_resample/<Source>` on a node of dahl to create:       
    + `Packages/EconData/data/<Source>_Coeffs.rda` and
    + `Packages/EconData/data/<Source>_Fitted.rda`.

Note that this command will need to be issued from a node of the cluster (e.g., node-00), not from `fs1.calvin.edu`.
`fs1` does not have a full install of R.
